From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-08-21 WOLFHPC15/article/article.tex
fix affiliation LIP
fix abstract

\numberofauthors{3} 
\author{
% 1st. author
\alignauthor
Julien Bigot\\
       \affaddr{CEA, Maison de la Simulation}\\
       \affaddr{USR 3441, CEA Saclay}\\
       \affaddr{91191 Gif-sur-Yvette, France}\\ % remove cedex
       \email{julien.bigot@cea.fr}
% 1st. author
\alignauthor
H\'el\`ene Coullon\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 All\'ee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{helene.coullon@inria.fr}
% 2nd. author
\and
\alignauthor
Christian P\'erez\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 All\'ee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{christian.perez@inria.fr}
}

@@

%----------------------------------------
\begin{abstract}
High performance heterogeneous architectures continuously evolve to be more powerfull. Such architectures also usually become more difficult to use efficiently. As a scientist is not a low level and high performance programming expert, Domain Specific Languages (DSLs) are a promising solution to automatically and efficiently write high performance codes. However, if DSLs ease programming for scientists, it seems that non-maintainability and non-portability problems are deported from the scientist to the DSL designer. In this paper is presented a new approach to improve maintainability and programming productivity of DSLs through the generation of a component-based parallel runtime. To study this approach the paper presents a proper new DSL for \emph{multi-stencil} programs, which is evaluated on the real-case shallow water equations.
\end{abstract}
%----------------------------------------

>>>>

\numberofauthors{3} 
\author{
% 1st. author
\alignauthor
Julien Bigot\\
       \affaddr{CEA, Maison de la Simulation}\\
       \affaddr{USR 3441, CEA Saclay}\\
       \affaddr{91191 Gif-sur-Yvette, France}\\ % remove cedex
       \email{julien.bigot@cea.fr}
% 1st. author
\alignauthor
H\'el\`ene Coullon\\
       \affaddr{INRIA, LIP}\\
       \affaddr{ENS Lyon, 46 All\'ee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{helene.coullon@inria.fr}
% 2nd. author
\and
\alignauthor
Christian P\'erez\\
       \affaddr{INRIA, LIP}\\
       \affaddr{ENS Lyon, 46 All\'ee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{christian.perez@inria.fr}
}

@@

%----------------------------------------
\begin{abstract}
  High performance architectures evolve continuously to be more powerful. Such architectures also usually become more difficult to use efficiently. As a scientist is not a low level and high performance programming expert, Domain Specific Languages (DSLs) are a promising solution to automatically and efficiently write high performance codes. However, if DSLs ease programming for scientists, maintainability and portability issues are deported from scientists to DSL designers. This paper deals with an approach to improve maintainability and programming productivity of DSLs through the generation of a component-based parallel runtime. To study it, the paper presents a  DSL for \emph{multi-stencil} programs, that is evaluated on a real-case of shallow water equations.
\end{abstract}
%----------------------------------------
